Future challenges for Research Software Engineering

### 2025-03-31 future_challenges_for_RSEng.tex
Break lines
Extend with a sentence to address both roles and suggest a future

We acknowledge but would also like to challenge the observations of the participants. We believe that ``we are standing on the shoulders of giants'': By reducing the complexity of individual software components, we are now able to develop systems of complexity and capability not previously possible, allowing the scientific community to address questions not previously in grasp. When it comes to teaching, it is true that students need to learn how to handle complexity, but it is also important to learn how to abstract from details (create black boxes) and build hierarchical systems from those abstractions and thereby manage complexity.

>>>>

We acknowledge but would also like to challenge the observations of the participants.
We believe that ``we are standing on the shoulders of giants'':
By reducing the complexity of individual software components,
we are now able to develop systems of complexity and capability not previously possible,
allowing the scientific community to address questions not previously in grasp.
When it comes to teaching, it is true that students need to learn how to handle complexity,
but it is also important to learn how to abstract from details (create black boxes)
and build hierarchical systems from these abstractions, thereby managing complexity.
It is clear that we need both RSEs that can dive deep into single projects of significant complexity,
as well as RSEs that can manage complex systems of almost black-box components,
and the future of RSE education should aim to prepare students for both roles.
